KeysarMouseTracking.csv

### 2016-05-12 analysis/cogSci_analysis.Rmd
Compile analysis script

```{r}
eDExp2 <- errorDExp2 %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  summarize(n = sum(criticalError)) %>%
  mutate(cond1 = as.numeric(n >= 1)) %>%
  mutate(cond2 = as.numeric(n >= 2)) #

@@

```{r}
numPlayersPerConditionExp2 = mouseDExp2 %>% 
  filter(critical == 1) %>% 
  filter(attemptNum == 0) %>% 
  group_by(gameid, condition, objectSet) %>% 
  summarize() %>% 
  group_by(condition, objectSet) %>% 
  summarize(total = n()) %>% 
  filter(condition == "exp")
```

@@

```{r}
itemInequalitiesExp2 <- errorDExp2 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp2, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)

@@

```{r}
library(binom)
Exp1Errs = itemInequalitiesExp1 %>%
  mutate(response = errorRate) %>%
  mutate(measure = "error") %>%
  do(mutate(., lower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               upper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, response, condition, lower, upper)

@@

Same thing for Exp 2

```{r}
library(binom)
Exp2Errs = itemInequalitiesExp2 %>%
  mutate(response = errorRate) %>%
  mutate(condition = "error") %>%
  do(mutate(., lower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               upper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, response, condition, lower, upper)

stat = function(data, indices) {
  d <- data[indices,]
  applicability = d %>%   
    group_by(objectSet) %>%
    summarize(m = .25 * mean(distractor)/mean(target))
  return(applicability$m)
}

@@

res = boot(data = Exp2Fitness, statistic = stat, R = 1000)
Exp2PlottingDF = data.frame(response = rep(0, 8),
                        upper = rep(0,8),
                        lower = rep(0,8),
                        objectSet = 1:8,
                        condition = rep("fitness", 8))
for (i in 1:8) {
  ci = boot.ci(res, type = "basic", index=i)
  Exp2PlottingDF[i,]$response = res$t0[i]
  Exp2PlottingDF[i,]$lower = ci$basic[4]
  Exp2PlottingDF[i,]$upper = ci$basic[5]
}

Exp2ItemwiseForPlot = rbind(Exp2PlottingDF, Exp2Errs)
g <- (ggplot(Exp2ItemwiseForPlot, aes(x = objectSet, y = response, 
                                      group = condition, fill = condition))
  + geom_bar(stat = "identity", position = "dodge")
  + geom_errorbar(aes(ymax = upper, ymin = lower), 
                  position = dodge , width = 0.25)
  + theme_bw(base_size = 16)
  + ylab("measure (z-scored)"))
g
```

```{r}
# within exp. correlations high
cor(Exp1Errs$response, Exp1PlottingDF$response)
cor(Exp2Errs$response, Exp2PlottingDF$response)

@@

```{r}
# heatMapForPlot$new_labels = as.factor(sapply(X = heatMapForPlot$objectSet, 
#                               FUN = function(v) {return(paste("Item", v))}))
# 
# g <- (ggplot(heatMapForPlot, aes(x = mouseX, y = mouseY, color = condition)) +
#       geom_vline(xintercept = c(0, 150,300,450, 600)) +
#       geom_hline(yintercept = c(0, 150,300,450, 600)) +
#       geom_point() +
#       geom_point(aes(x = begTargetX, y = begTargetY), size = 20,
#                  shape = 4, color = "black", show_guide = FALSE) +
#       geom_point(aes(x = begDistrX, y = begDistrY), size = 20,
#                  shape = 4, color = "grey50", show_guide = FALSE) + 
#       theme(panel.grid.major = element_blank(), 
#             panel.grid.minor = element_blank()) +
#       xlim(0, 600) +
#       ylim(0, 600) +
#       theme(aspect.ratio = 1) +
#       facet_wrap(~ new_labels, nrow = 2))
# g
```

>>>>

```{r}
eDExp1 <- errorDExp1 %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  summarize(n = sum(criticalError)) %>%
  mutate(cond1 = as.numeric(n >= 1)) %>%
  mutate(cond2 = as.numeric(n >= 2))

eDExp2 <- errorDExp2 %>%
  filter(attemptNum == 0) %>%
  group_by(gameid, condition) %>%
  summarize(n = sum(criticalError)) %>%
  mutate(cond1 = as.numeric(n >= 1)) %>%
  mutate(cond2 = as.numeric(n >= 2)) #

@@

```{r}
numPlayersPerConditionExp1 = mouseDExp1 %>% 
  filter(critical == 1) %>% 
  filter(attemptNum == 0) %>% 
  group_by(gameid, condition, objectSet) %>% 
  summarize() %>% 
  group_by(condition, objectSet) %>% 
  summarize(total = n()) %>% 
  filter(condition == "exp")

numPlayersPerConditionExp2 = mouseDExp2 %>% 
  filter(critical == 1) %>% 
  filter(attemptNum == 0) %>% 
  group_by(gameid, condition, objectSet) %>% 
  summarize() %>% 
  group_by(condition, objectSet) %>% 
  summarize(total = n()) %>% 
  filter(condition == "exp")
```

@@

```{r}
itemInequalitiesExp1 <- errorDExp1 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp1, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)
itemInequalitiesExp1[1,2:4] = c(0, itemInequalitiesExp1[1,]$total, 0)

itemWiseTestExp1 <- chisq.test(itemInequalitiesExp1[-c(1,4,5)])

itemInequalitiesExp2 <- errorDExp2 %>%
  filter(condition == "exp") %>%
  filter(criticalError == 1) %>%
  filter(attemptNum == 0) %>%
  group_by(objectSet) %>%
  tally() %>%
  right_join(numPlayersPerConditionExp2, by = c('objectSet')) %>%
  mutate(objectSet = objectSet,
         errorCount = n, 
         correctCount = total - n) %>%
  mutate(errorRate = errorCount / (errorCount + correctCount)) %>%
  select(objectSet, errorCount, correctCount, errorRate, total)

@@

```{r}
library(binom)
Exp1Errs = itemInequalitiesExp1 %>%
  mutate(response = errorRate) %>%
  mutate(measure = "error") %>%
  do(mutate(., lower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               upper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, response, measure, lower, upper)

@@

Alternatively, could make a scatter plot?

```{r}
library(binom)
Exp1Errs = itemInequalitiesExp1 %>%
  do(mutate(., errorLower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               errorUpper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, errorRate, errorLower, errorUpper)

stat = function(data, indices) {
  d <- data[indices,]
  applicability = d %>%   
    group_by(objectSet) %>%
    summarize(m = mean(distractor)/mean(target))
  return(applicability$m)
}

res = boot(data = Exp1Fitness, statistic = stat, R = 1000)
Exp1PlottingDF = data.frame(fitness = rep(0, 8),
                        fitnessUpper = rep(0,8),
                        fitnessLower = rep(0,8),
                        objectSet = 1:8)
for (i in 1:8) {
  ci = boot.ci(res, type = "basic", index=i)
  Exp1PlottingDF[i,]$fitness = res$t0[i]
  Exp1PlottingDF[i,]$fitnessLower = ci$basic[4]
  Exp1PlottingDF[i,]$fitnessUpper = ci$basic[5]
}

Exp1ItemwiseForPlot = left_join(Exp1Errs, Exp1PlottingDF, by = c("objectSet"))
g <- (ggplot(Exp1ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point() 
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower), 
                  width = 0.05)
  + geom_smooth(method = "lm")
  + theme_bw(base_size = 16) 
  + ggtitle("Exp.1 Item-Wise Error")
  + ylab("ratio (scaled)"))
g
#ggsave("../../writing/cogsci-submission/images/itemWiseFitness.pdf")
```
Same thing for Exp 2

```{r}
library(binom)
binomStat = stat = function(data, indices) {
  d <- data[indices,]
  prop = d %>%   
    group_by(objectSet) %>%
    summarize(m = mean(distractor)/mean(target))
  return(applicability$m)
}

Exp2Errs = itemInequalitiesExp2 %>%
  do(mutate(., errorLower = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$lower,
               errorUpper = binom.confint(.$errorCount, .$total, 
                                     method = "bayes")$upper)) %>%
  select(objectSet, errorRate, errorLower, errorUpper)

stat = function(data, indices) {
  d <- data[indices,]
  applicability = d %>%   
    group_by(objectSet) %>%
    summarize(m = mean(distractor)/mean(target))
  return(applicability$m)
}

@@

res = boot(data = Exp2Fitness, statistic = stat, R = 1000)

Exp2PlottingDF = data.frame(fitness = rep(0, 8),
                        fitnessUpper = rep(0,8),
                        fitnessLower = rep(0,8),
                        objectSet = 1:8)
for (i in 1:8) {
  ci = boot.ci(res, type = "basic", index=i)
  Exp2PlottingDF[i,]$fitness = res$t0[i]
  Exp2PlottingDF[i,]$fitnessLower = ci$basic[4]
  Exp2PlottingDF[i,]$fitnessUpper = ci$basic[5]
}

Exp2ItemwiseForPlot = left_join(Exp2PlottingDF, Exp2Errs, by = c("objectSet")) %>%
  mutate(experiment = "Exp. 2") %>%
  rbind(Exp1ItemwiseForPlot %>% mutate(experiment = "Exp. 1"))

g <- (ggplot(Exp2ItemwiseForPlot, aes(x = fitness, y = errorRate))
  + geom_point(aes(color = experiment))
  + geom_errorbarh(aes(xmax = fitnessUpper, xmin = fitnessLower,
                       color = experiment), 
                  height = 0.01)
  + geom_errorbar(aes(ymax = errorUpper, ymin = errorLower,
                     color = experiment), 
                width = 0.05)
  + geom_smooth(method = "lm",colour="black")
  + theme_bw(base_size = 16)
  + theme(aspect.ratio=1)
  + ylab("Error rate")
  + xlab("Label fitness of distractor vs. target"))
g
ggsave("~/Repos/keysar_replication/writing/cogsci-revision/images/itemWiseFitness.pdf")
```

```{r}
summary(lm(errorRate ~ fitness * experiment, data = Exp2ItemwiseForPlot))

# within exp. correlations high
cor(Exp1Errs$response, Exp1PlottingDF$response)
cor(Exp2Errs$response, Exp2PlottingDF$response)

@@
